---
title: "Sensitivity Analysis"
author: "Talia Borofsky"
date: "5/31/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(car)
library(dplyr)
library(aod)
library(ggplot2)
library(latex2exp)
library(olsrr)
library(lmtest)
library(zeallot)
library(ROSE) # for roc curve
library(RVAideMemoire) # library that has spearman.ci function...gets confidence intervals on spearman using bootstrap

caption_at_bottom <- function(x,fn ) {
  # x is output from stargazer, fn is filename
  cap <- grep("\\\\caption", x)
  lab <- grep("\\\\label", x)
  last <- grep("\\\\end\\{table", x)
  cat(
    paste(
      c(x[-last], x[cap], x[lab], x[last])[-c(cap, lab)]
    , collapse = "\n")
  , "\n", file = fn, append = TRUE)
}
p_lratiotest <- function(mylogit){
  result <- with(mylogit, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
  return(result)
}
classification_table <- function(mod,Y){
  
  Yhat <- fitted(mod)
  thresh <- 0.5
  YhatFac <- cut(Yhat, breaks = c(-Inf, thresh, Inf), labels = c("FALSE", "TRUE"))
  cTab <- table(Y, YhatFac)
  addmargins(cTab)
}
```

# K > 1/2, D = 0, unequal equilibrium
$$
\text{sign}(C_D) = \text{sign} \left( \frac{2K-1}{K} -3 \left(u_1^2 + \left( \frac{2K-1}{K} - u1 \right)^2 \right)+2 \left(u_1^3 + \left( \frac{2K-1}{K} - u1 \right)^3 \right)\right)
$$


```{r}
K<-seq(1/2,0.99,length=1000)
u<-seq(0,1,length=1000)
z<-outer(K,u,function(K,u) (2*K-1)/K -3*u^2 -3*((2*K-1)/K -u)^2 + 2*u^3 + 2*((2*K-1)/K -u)^3)
require(genridge)
filled.contour(K,u,z, levels = c(-1000,0,1000), col = c("blue","white"), xlab = "K",ylab = TeX("$u_1$"))


grid <- expand.grid(K = seq(1/2,0.99,length.out=1000),u = seq(0,1,length.out=1000))
f <- function(K,u) (2*K-1)/K -3*u^2 -3*((2*K-1)/K -u)^2 + 2*u^3 + 2*((2*K-1)/K -u)^3
f2 <- function(K,u) (2*K-1)/K - u
grid$filled <- (f(grid$K,grid$u)>=0) 
grid$filled[(f2(grid$K,grid$u)<0)|(f2(grid$K,grid$u)>1)] = NA
p<- ggplot(grid) + geom_tile(aes(x=K,y=u,fill=filled))  + theme_classic() + labs(x=TeX("$K$"),y = TeX("$u_1$"))+ theme(legend.position = "none") + scale_fill_brewer(palette="Set1", na.value="white")

p
ggsave("D0Unequal_C_D.png", plot = p)
#red means C_D < 0, turquoise means C_D > 0
```


```{r dframes, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load the Unique Equilibria

uniqueEquilibria <- read.csv('UniqueEquilibriaDF.csv', as.is=TRUE)


# helped to round D values
uniqueEquilibria$D <-round(uniqueEquilibria$D,digits = 10)

# setting up the columns that indicate whether more/less social learning evolves, more/less conformity evolves
uniqueEquilibria$x_pos_invades <- uniqueEquilibria$C_s > 0
uniqueEquilibria$x_neg_invades <- uniqueEquilibria$C_s < 0
uniqueEquilibria[uniqueEquilibria=="True"]=TRUE
uniqueEquilibria[uniqueEquilibria=="False"]=FALSE
### deal with equilibria for which lambda* = 1

# rename and do rest of changes to eqData
eqData <- uniqueEquilibria

# I need to check on calculating C_s
fs <- function(s,mu) dnorm(s,mean=mu,sd=1)
fms <- function(s,mu) dnorm(-s,mean=mu,sd=1)
phifun<-function(u) u*(1-u)*(2*u-1)
get_C_s <- function(s,mu,W,D,u1,u2,r1,r2) (1/W)*(-fs(s,mu) + (fs(s,mu)+fms(s,mu))*(r1*(u1 + D*phifun(u1)) + r2*(u2+D*phifun(u2)) ) )
C_s = get_C_s(eqData$s, eqData$mu, eqData$W, eqData$D, eqData$u1eq, eqData$u2eq, eqData$r1eq, eqData$r2eq)
eqData$C_s = C_s

# remove the small very s, D values
eqData <- eqData %>% filter(s != 0.01) %>% filter(D != -0.01) %>% filter(D!=0.01)

# remove values where s = 0 and D > 0
eqData <- eqData %>% filter(!(s==0&D!=0))

# fix equilibria in which lambdastar = 1 but actually internally stable
attach(eqData)
mask =(beta==0)&(D==0)&(pc==0)&(K>0) # this equilibria might have lambda* = 1, but is actually internally stable
eqData[mask,]$URstable = 1
detach(eqData)
# only use equilibria that are internally stable
eqData <- eqData %>% filter(URstable == 1)

# If C_s is negative when K = 0, then set it to 0
eqData[(eqData$K==0)&(eqData$C_s<0),]$C_s = 0

# label by whether Increased Social Leanring Invades, Decreased invades, or stable
eqData$signC_s <- factor(sign(eqData$C_s))
# thre are about 16 places where r says C_s = 0 but it's actually negative
eqData$signC_s[eqData$signC_s==0] = -1

eqData$signC_D <- factor(eqData$C_D)


# add column for learning success 

eqData$learningSuccess = eqData$u1eq + eqData$u2eq # portion of foragers that learn how to find food


# Make separate data frames for whether D \geq 0 or D \leq 0 and for whether or not u1 = u2
eqDataPos = eqData %>% filter(D>=0)
eqDataPos_UnEqual <-  eqDataPos %>% filter(difference > 0)
eqDataPos_Equal = eqDataPos %>% filter(difference==0)
# D < 0
eqDataNeg = eqData %>% filter(D<=0)
eqDataNeg_UnEqual = eqDataNeg %>% filter(difference>0)
eqDataNeg_Equal = eqDataNeg %>% filter(difference==0)

# number of rows where u1 \neq u2 and D < 0: none
print(nrow(eqData[eqData$D < 0 & eqData$difference > 0,]))
uniqueEquilibria %>% filter(URstable==-1)
head(uniqueEquilibria)
```

# Numerical Analysis
## Data
The dataframes I work with are:

* *eqData* - the dataframe of all the parameter and equilibrium combinations that are internally stable
* *eqDataPos* - the dataframe of all the parameter and equilibrium combinations that are internally stable such that $D \geq 0$
* *eqDataNeg* -  the dataframe of all the parameter and equilibrium combinations that are internally stable such that $D < 0$
* *eqDataPos_Equal* - eqDataPos, but only the equilibria in which $|\hat{u_1} - \hat{u_2}| = 0$. 
* *eqDataPos_UnEqual* - eqDataPos, but only the equilibria in which $|\hat{u_1} - \hat{u_2}| > 0$. -

The important columns of the dataframes are:

* The parameters: K, pc ($\pi_C$), s, mu ($\mu$), beta ($\beta$), 
* Values found through iteration: u1eq ($\hat{u_1}$), u2eq ($\hat{u_2}$), Weq ($\hat{W}$)
* Values calculated from the equilibria: difference ($|\hat{u_1} - \hat{u_2}|$), learningSuccess ($\hat{u_1} + \hat{u_2}$), xInvades ($C_s>0$, so more social learning $\delta_K > 0$ invades), y_pos_invades ($C_D > 0$, so more conformity $\delta_D > 0$ invades), and y_neg_invades ($C_D < 0$, so more anticonformity $\delta_D < 0$ invades).  Note that we only work with y_pos_invades when $D \geq 0$, and we only work with y_neg_invades when $D \leq 0$.

## Section 1:Anticonformity, Learning Success, and Mean Population Fitness -->
In this section, we seek to understand what advantage anticonformity confers. We use Spearman's rank correlation coefficient to examine the relationships between anti-conformity and mean population fitness, $\hat{W}$, and learning success, $\hat{u_1} + \hat{u_2}$, without accounting for social learning $K$. The linear regression of $D, D < 0$ onto both $\hat{W}$ and learning success $\hat{u_1} + \hat{u_2}$ has $R^2 < .01$.




```{r anticonformity W learning success spearman, echo=FALSE, warning=FALSE, message=FALSE}

corWeq <- cor.test(eqDataNeg$D, eqDataNeg$Weq, method = "spearman"); print(corWeq)

corlearn <- cor.test(eqDataNeg$D, eqDataNeg$learningSuccess, method = "spearman"); print(corlearn)
spearman.ci(eqDataNeg$D, eqDataNeg$learningSuccess, nrep = 1000, conf.level = 0.999)
```

Using a Spearman's Rank Correlation Test, we cannot reject the null hypothesis that there is no monotonic relationship between  $D$ and $\hat{W}$ for $D < 0$ ($S = `r round(corWeq$statistic,3)`, p = `r round(corWeq$p.value,3)`$), but there is a significant but small monotonic relationship between $D$ and learning success: as anticonformity increases ($D$ becomes more negative), learning success slightly increases ($\rho_s =`r round(corlearn$estimate,3)`, p < `r round(corlearn$p.value,3)`$)


For comparison, look at how conformity affects these values
```{r}
#mpos <- lm(data=eqDataPos, Weq ~ D)
#summary(mpos)

cor.test(eqDataPos$Weq, eqDataPos$D, method = "spearman")
spearman.ci(eqDataPos$D, eqDataPos$Weq, nrep = 1000, conf.level = 0.999)

cor.test(eqDataPos$learningSuccess, eqDataPos$D, method = "spearman")
spearman.ci(eqDataPos$D, eqDataPos$learningSuccess, nrep = 1000, conf.level = 0.999)

```

## Section 2: Positive feedback between the evolution of social learning and learning success
First, does more social learning correspond with more learning success (regardless of $\pi_c$)?

We try a linear regression of $K$ on learning success $\hat{u_1} + \hat{u_2}$

```{r sec3 lin reg, echo=FALSE, warning=FALSE, message=FALSE}

m1 <- lm(learningSuccess ~ K, data = eqData)
summary(m1)

```
Social learning seems to correlate with more learning success, though the relationship is not linear.
Since the relationship is not linear, we try a spearman rank correlation
```{r sec3 spearman, echo=FALSE, warning=FALSE, message=FALSE}
ctest <- cor.test(eqData$K, eqData$learningSuccess, method = "spearman")
ctest
spearman.ci(eqData$K, eqData$learningSuccess, nrep = 1000, conf.level = 0.999)

```

We see a strong and significant positive correlation ($\rho = .483, p < .001$)


However, the logistic regression has a very poor fit (indicated by the log likelihood value),

Instead, we can look at whether learning success values are distributed differently when $C_s >0$, $C_s = 0$, and $C_s < 0$.

```{r}
attach(eqData)
# when s = 0, we have a bunch of C_s = 0 values...which should not be like that!
numerator_correctC_s  <- function(mu,u,beta) -dnorm(0, mean=mu, sd=1) + 4*dnorm(0,mean=mu,sd=1)*(1-beta*u)*u
numC_s <- numerator_correctC_s(eqData$mu, eqData$u1eq, eqData$beta)

aov <- aov(learningSuccess~signC_s)
summary(aov)
plot(aov)
# require(onewaytests)
# # heteroscedastic and non-normal so use Kruskal Wallis test
# kt <- kruskal.test(learningSuccess~signC_s,data=eqData)
# 
# posthoc <- pairwise.wilcox.test(learningSuccess, signC_s, p.adjust.method='none')
# posthoc
t <- TukeyHSD(aov)
plot(t)

unique(sign(eqData$C_s))
eqDataCs0 <- eqData %>% filter(C_s == 0)
numerator_correctC_s  <- function(mu,u,beta) -dnorm(0, mean=mu, sd=1) + 4*dnorm(0,mean=mu,sd=1)*(1-beta*u)*u
numC_s <- numerator_correctC_s(eqDataCs0$mu, eqDataCs0$u1eq, eqDataCs0$beta)
# it's rounding!

#maxs$Tukey = c('a','b','c')
p.b <- ggplot(data=eqData, aes(x=signC_s,y=learningSuccess,fill=signC_s))+geom_violin(adjust=1) + theme_classic() + labs(x=TeX("$sign(C_s)$"), fill = TeX("$sign(C_s)$"), y = TeX("\\hat{u_1} + \\hat{u_2}"),fontsize=20) + theme(legend.position = "none") + theme(text = element_text(size = 20)) 

p.b
ggsave("LearnSuccess_SignCs.png", plot = p.b)

p.his <- ggplot(data=eqData, aes(x=learningSuccess))+geom_histogram(binwidth=.01) + theme_classic() + theme(text = element_text(size = 20)) + labs(x = "Learning Success")
p.his
ggsave("LearnSuccess_his.png", plot = p.his)

```
Thus increased social learning tends to invade when learning success is high, especially when $\hat{u_1} + \hat{u_2} = 1$, while the learning success at equilibria for which decreased social learning envades has a bimodal distribution: learning success is either high or low. Furthermore, $C_s \new 0$ for all equilibria in which $K = 0$. 

These trends are slightly different when we analyze equal and unequal equilibria separately. Here are the violin plots when $\hu{1} = \hu{2}$ and $D \geq 0$. I specify $D \geq 0$ because we want to compare the equal and unequal equilibria cases, but equilibria are only unequal when $D \geq 0$. Each violin is labeled with the number of equilibria it describes.
```{r}
abs_max = max(learningSuccess)
maxs <- eqDataPos_Equal %>% group_by(signC_s ) %>% summarise(learningSuccess=max(learningSuccess) + 0.05 * abs_max, n = length(signC_s)) 


p.b <- ggplot(data=eqDataPos_Equal, aes(x=signC_s,y=learningSuccess,fill=signC_s))+geom_violin(adjust=1) + theme_classic() + labs(x=TeX("$sign(C_s)$"), fill = TeX("$sign(C_s)$"), y = TeX("\\hat{u_1} + \\hat{u_2}"),fontsize=20)+ geom_text(data=maxs,aes(label=n))

p.b
```
Here are violin when $\hu{1} \neq \hu{2}$ and $D \geq 0$. 
```{r}
abs_max = max(learningSuccess)
maxs <- eqDataPos_UnEqual %>% group_by(signC_s ) %>% summarise(learningSuccess=max(learningSuccess) + 0.05 * abs_max, n = length(signC_s)) 


p.b <- ggplot(data=eqDataPos_UnEqual, aes(x=signC_s,y=learningSuccess))+geom_violin(position=position_dodge(1)) + theme_classic() + labs(x=TeX("$sign(C_s)$"), y = TeX("\\hat{u_1} + \\hat{u_2}"),fontsize=20)+ geom_text(data=maxs,aes(label=n)) + ylim(0,1.3)

p.b

p.his <- ggplot(data=eqDataPos_UnEqual, aes(x=learningSuccess))+geom_histogram(binwidth=.01) + theme_classic()
p.his
```

$C_s \neq 0$ for all equilibria in which $\hu{1} \neq \hu{2}$. Less social learning only invades when $\hu{1} + \hu{2}$ is high., but also most of the equilibria in which $\hu{1} \neq \hu{2}$ have high learning success.


Next, I predict that if it is harder to learn individually correctly, then social learning should be even more beneficial to learning success. I use the indicator variable mu_pos, which is 1 when $\mu \geq 0$ and 0 otherwise and do a linear regression of the effect of the interaction between $K$ and mu_pos on learning success.

```{r sec3 mu, echo=FALSE, warning=FALSE, message=FALSE}
# still have eqData attached

mu_pos = eqData$mu>=0
eqData$mu_pos = mu_pos
m.mu <- lm(learningSuccess ~K*mu_pos, data=eqData)
summary(m.mu)
stargazer(m.mu, type="text")
c(m.int, m.K, m.mu_pos, m.mu_pos.K) %<-% m.mu$coefficients
```
So when $\mu \geq 0$,
$$
\hat{u_1} + \hat{u_2} = .934 + 0.002K
$$
and when $\mu < 0$,
$$
\hat{u_1} + \hat{u_2} = .227 + .619 K
$$
although the $R^2 - .479$, which is rather low.

Now how does $\mu$ affect whether learning success selects for social learning? Again use the indicator variable mu_pos. Then running a logistic regression with the covariates being the interaction of learning success and mu_pos, and the dependent variable being whether increased social learning invades:

```{r chi-squared, warning=F,message=F}
# mupos is 1 if > 0, 0 if <=0
mu_nonneg = factor(eqData$mu>=0)
signC_s = factor(eqData$signC_s)
SocLearnMuTable <- table(signC_s, mu_nonneg)
SocLearnMuTable


chisq.test(SocLearnMuTable)


datuse <- data.frame(mu_nonneg, signC_s)
datuse <- datuse %>% group_by(mu_nonneg, signC_s) %>% count()

p <- ggplot(datuse, aes(x = mu_nonneg, y = n, fill = signC_s)) + geom_bar(position="stack",stat="identity") + labs(y="Num Equilibria", fill = TeX("$\\sign(C_s)$"), x = TeX("$\\mu \\geq 0$")) + theme_classic()+ theme(text = element_text(size = 20)) 
p
ggsave("Figures/MuSocLearnStack.png", plot = p)
```


## Section 3: The effects of social learning and conformity on behavioral preference

I hypothesized that social learning ($K$), conformity ($D$), and in particularly the product of the two ($KD$) should cause larger behavioral preference $$ |\hat{u_1} - \hat{u_2}|$$. 
In this case behavioral preference was measured from the equilibrium that had the maximum $$\mid \hat{u_1} – \hat{u_2} \mid $$ for each set of parameters.
Doing a linear regression of behavioral preference in relation to $K$, $D$, and $KD$, the coefficients are described in the following table:

```{r sec4, echo=FALSE, warning=FALSE, message=FALSE}
#eqdata already attached
eqData.maxDiff <- eqDataPos %>%
  group_by(s,K,D,mu,beta) %>%
  summarise(max_diff = max(difference)) %>% 
  mutate(KD = K*D)

attach(eqData.maxDiff)
m <- lm(max_diff ~ K*D, data=eqData.maxDiff)
summary(m)
stargazer(m, type = "text", covariate.labels = c("K","D", "KD"), dep.var.labels = "Maximum Behavioral Preference")
plotH2 <- ggplot(data = eqData.maxDiff, mapping = aes(x = KD, y = max_diff)) + geom_point(size = 3, shape = 1) + theme_bw()
plotH2 <- plotH2 + labs(x = TeX("$KD$"), y = "Max Behavioral Preference")  
plotH2
ggsave("Figures/plotH2.png", plot = plotH2) # still calling it H2 because when I originally named these plots I called this section was hypothesis 2
```
Social learning has  a positive effect as expected, but conformity has a negative effect, which is weird. Finally, as expected, social learning and conformity together increase behavioral preference more then social learning alone. 

## Section 4: The effects of food depletion and behavioral preference on learning success and mean population fitness.

I expected that increasing predation, $\beta$, would suppress learning success $\hat{u_1} + \hat{u_2}$ , 
and for this effect to be amplified by behavioral preference $|\hat{u_1} - \hat{u_2}|$.


I check the effect of $\beta$ and its interaction with an indicator variable called "isDiff" that is 1 when $\hat{u_1} \neq \hat{u_2}$, 0 otherwise. *Question: Should I be doing pairwise comparisons between equilibria within each set of parameters $(\mu,s,D,\beta)$?*

```{r sec5, echo=FALSE, warning=FALSE, message=FALSE}

attach(eqData)
isDiff = difference > 0
m1 <- lm(Weq ~ isDiff*beta)
c(m1.int, m1.isDiff, m1.beta, m1.isDiff.beta) %<-% m1$coefficients
stargazer(m1, type = "text",covariate.labels = c("isDiff=TRUE", "beta", "beta(isDiff=TRUE)"), dep.var.labels = "Mean Pop Fitness")
library(ggplot2)


datUse = eqDataPos %>% mutate(betadiff = beta*difference)
plotH1.LS <- ggplot(data = datUse, mapping = aes(x = difference, y = learningSuccess, color = beta)) + geom_point(size = 3, alpha = 0.5) + theme_bw()+ labs(x = TeX("$|\\hat{u_1} - \\hat{u_2}|$"), y = TeX("$\\hat{u_1} + \\hat{u_2}$"), color = TeX("$\\beta$")) + theme(text = element_text(size = 20)) 
plotH1.LS
ggsave("Figures/plotH1_LS.png", plot = plotH1.LS)
```

So if $\hat{u_1} \neq \hat{u_2}$,
$$
\hat{W} = `r m1.int + m1.isDiff` + `r m1.beta + m1.isDiff.beta` \beta + \text{residuals}
$$
and if $\hat{u_1} = \hat{u_2}$,
$$
\hat{W} = `r m1.int` + `r m1.beta` \beta + \text{residuals}.
$$

As for learning success, a linear regression with isDiff and beta as covariates is described by the following table:
```{r sec5 ls, echo=FALSE, warning=FALSE, message=FALSE}
m2 <- lm(learningSuccess ~ isDiff*beta)
c(m2.int, m2.isDiff, m2.beta, m2.isDiff.beta) %<-% m2$coefficients
stargazer(m2, type = "text",covariate.labels = c("isDiff=TRUE", "beta", "beta(isDiff=TRUE)"), dep.var.labels = "Learning Success")



plot.H1.W <- ggplot(data = datUse, mapping = aes(x = difference, y = Weq, color = beta)) + geom_point(size=3, alpha = 0.5) + theme_bw() + labs(x = TeX("$|\\hat{u_1} - \\hat{u_2}|$"), y = TeX("$\\hat{W}$"), color = TeX("$\\beta$")) 
plot.H1.W
#ggsave("Figures/plotH1_W.png", plot = plot.H1.W)

```
So if $\hat{u_1} \neq \hat{u_2}$,
$$
\hat{u_1} + \hat{u_2}= `r m2.int + m2.isDiff` + `r m2.beta + m2.isDiff.beta` \beta + \text{residuals}
$$
and if $\hat{u_1} = \hat{u_2}$,
$$
\hat{u_1} + \hat{u_2} = `r m2.int` + `r m2.beta` \beta + \text{residuals}
$$


However, the $R^2 on these are terrible.

Correlations when $\hu{1} = \hu{2}$
```{r, message=F}
attach(eqData)
isDiff = difference > 0
cor.test(eqData$Weq[!isDiff],eqData$beta[!isDiff], method = "spearman")
spearman.ci(eqData$Weq[!isDiff],eqData$beta[!isDiff],nrep=1000,conf.level=0.999)


cor.test(eqData$Weq[isDiff], eqData$beta[isDiff], method = "spearman")
spearman.ci(eqData$Weq[isDiff],eqData$beta[isDiff],nrep=1000,conf.level=0.999)
```


```{r, message=F}
attach(eqData)

isDiff = difference > 0

cor.test(eqData$learningSuccess[!isDiff],eqData$beta[!isDiff], method = "spearman")

cor.test(eqData$learningSuccess[isDiff], eqData$beta[isDiff], method = "spearman")
spearman.ci(eqData$learningSuccess[isDiff], eqData$beta[isDiff],nrep=1000,conf.level=0.999)
```
## Section 5: Food depletion and behavioral preference
First I try a linear regression

```{r sec6 depletion and behavior pref, echo=FALSE, warning=FALSE, message=FALSE}

m <- lm(data = eqData, difference ~ beta)
stargazer(m, type = "text", dep.var.labels = "behavioral preference")
cortest <- cor.test(eqData$beta, eqData$difference, alternative = "less")
cortest
confint(cortest)
install.packages('RVAideMemoire')
require(RVAideMemoire) # library that has spearman.ci function...gets confidence intervals on spearman using bootstrap
s
cortest <- cor.test(eqData$beta, eqData$difference, method = "spearman")
cortest
spearman.ci(eqData$beta, eqData$difference, nrep = 1000, conf.level = 0.999)
```
For the linear model, the $R^2$ is too low. I use Spearman's rank instead, and find the correlation between $\beta$ and behavioral preference is $\rho = `r cortest$estimate`, p = `r cortest$p.value`$. The $\rho$ value is close to the coefficient of $\beta$ in the linear model, and I'm wondering if I can still use the linear model to say that increasing predation $\beta$ makes the population show less behavioral preference.

## Section 6: Food depletion hampers the evolution of social learning and conformity
```{r D0}
eqDataD0 <- eqData %>% filter(D==0)
eqDataD0$mu_pos <- eqDataD0$mu >=0

set.seed(5)
eqDataD0.1 <- eqDataD0 %>% filter(mu_pos==TRUE)
eqDataD0.2 <- eqDataD0 %>% filter(mu_pos==FALSE)
cortest <- cor.test(eqDataD0$C_s, eqDataD0$beta, method="spearman")
cortest
spearman.ci(eqDataD0$C_s, eqDataD0$beta, nrep = 1000, conf.level=0.999)
set.seed(5)
cortest1 <- cor.test( eqDataD0.1$C_s, eqDataD0.1$beta, method = "spearman")
cortest1
spearman.ci(eqDataD0.1$beta, eqDataD0.1$C_s, nrep = 1000, conf.level = 0.999)
set.seed(5)
cortest2 <- cor.test( eqDataD0.2$C_s, eqDataD0.2$beta, method = "spearman")
cortest2
spearman.ci(eqDataD0.2$beta, eqDataD0.2$C_s, nrep = 1000, conf.level = 0.95)

p <- ggplot(data = eqDataD0, aes(x=beta,y=C_s,color=mu_pos )) + geom_jitter() + geom_smooth(method=lm,se=FALSE, fullrange=TRUE) + theme_classic()  + labs(x=TeX("$\\beta$"), y=TeX("$C_s$"), colour = TeX("$\\mu \\geq 0$"),fontsize=20) + scale_color_manual(breaks = c(FALSE, TRUE),values=c("red", "#56B4E9")) + geom_hline(yintercept=0,linetype="dashed", size=0.5)+ theme(text = element_text(size = 20)) 
p
ggsave("Figures/D0jitter.png", plot = p)

eqDataD0_x_pos <- eqDataD0 %>% filter(x_pos_invades==TRUE)
nrow(eqDataD0)
nrow(eqDataD0_x_pos)
max(eqDataD0_x_pos$beta)
```

I use logistic regressions to examine the effect of food depletion, in combination with the indicator variable isDiff (which is 1 if $\hat{u_1}\neq \hat{u_2}$, 0 if $\hat{u_1} = \hat{u_2}$), on whether $C_s > 0$ and on whether $C_D > 0$. The logistic regression on whether increased conformity invades, $C_D > 0$, is only conducted on equilibria in which $D \geq 0$.

``` {r sec7, echo=FALSE, warning=FALSE, message=FALSE}
# Does increasing K from 0 cause there to be a difference between u_1 and u_2? A: no
smallK <- eqData %>% filter(round(K,2) ==0.01) %>% filter(difference>0)

# As beta increases, and u1 \neq u2, then conformity and social learning will be less likely to invade
# use variable isDiff


eqDataPos$isDiff = eqDataPos$difference>0
eqData$isDiff = eqData$difference>0

model.y <- glm(data = eqDataPos, y_pos_invades ~ beta*isDiff, family = binomial(link="logit"))
model.x <- glm(data = eqData, xInvades ~ beta*isDiff, family = binomial(link = "logit"))
stargazer(model.x, type = "text", dep.var.labels = "Increased social learning invades", covariate.labels = c("beta", "isDiff = TRUE", "beta(isDiff=TRUE)"))
lrtest(model.x)
stargazer(model.y, type = "text", dep.var.labels = "Increased conformity invades", covariate.labels = c("beta", "isDiff = TRUE", "beta(isDiff=TRUE)"))
lrtest(model.y)


```
It seems beta and the indicator variable of whether $\hat{u_1} \neq \hat{u_2}$ do not have any effect on whether increased conformity invades.


HOWEVER, these logistic regressions are terrible. I'll have to do the violin plots method instead
```{r}

#maxs$Tukey = c('a','b','c')

p.b <- ggplot(data=eqData, aes(x=signC_s,y=beta,fill=isDiff))+geom_boxplot(adjust=1, scale = "count") + theme_classic() + labs(x=TeX("$sign(C_s)$"), y = TeX("$\\beta$"),fontsize=20)+ theme(text = element_text(size = 20))  #+ geom_text(data=maxs,aes(label=Tukey))

p.b <- p.b + scale_fill_discrete(name = "Behavioral Preference", labels = c("no behavioral preference","positive behavioral preference"))
p.b
ggsave("Figures/BehavPref_boxplot.png", plot = p.b)
aov <- aov(beta ~ signC_s*isDiff)
summary(aov)

aov1 <- aov(beta~ factor(isDiff), subset=signC_s==1)
summary(aov1)
TukeyHSD(aov1)
```



```{r}

attach(eqDataPos)
isDiff = difference>0

dat = eqDataPos %>% filter(difference>0)

p.b <- ggplot(data=dat, aes(x=factor(y_pos_invades),y=beta))+geom_boxplot() + theme_classic() + labs(x="Increased Conformity Evolves", y = TeX("$\\beta$"),fontsize=20) + theme(text = element_text(size = 20),axis.title.x = element_text(vjust=-1.1)) #+ geom_text(data=maxs,aes(label=Tukey))

p.b

ggsave("Figures/BehavPref_boxplot_D.png", plot = p.b)

p.b <- ggplot(data=dat, aes(x=factor(y_neg_invades),y=beta))+geom_boxplot() + theme_classic() + labs(x="Decreased Conformity Evolves", y = TeX("$\\beta$"),title = TeX("$\\hat{u_1} \\neq \\hat{u_2}$"),fontsize=20) + theme(text = element_text(size = 20),axis.title.x = element_text(vjust=-1.1)) #+ geom_text(data=maxs,aes(label=Tukey)) 

p.b

ggsave("Figures/BehavPref_boxplot_pos_diff_Dless.png", plot = p.b)

p.b <- ggplot(data=eqData %>% filter(difference==0), aes(x=factor(y_neg_invades),y=beta))+geom_boxplot() + theme_classic() + labs(x="Decreased Conformity Evolves", y = TeX("$\\beta$"), title = TeX("$\\hat{u_1} = \\hat{u_2}$"),fontsize=20) + theme(text = element_text(size = 20),axis.title.x = element_text(vjust=-1.1)) #+ geom_text(data=maxs,aes(label=Tukey))

p.b

ggsave("Figures/BehavPref_boxplot_pos_nodiff_Dless.png", plot = p.b)


# aov <- aov(beta ~ factor(signC_D)*factor(isDiff))
# summary(aov)
# aov1 <- aov(beta~signC_D)
# TukeyHSD(aov1)
# aov2 <- aov(beta~signC_D, subset=isDiff) #when hu1 \neq hu2
# aov3 <- aov(beta~signC_D, subset=!isDiff) #when hu1 = hu2
# t <- TukeyHSD(aov)
# t$`factor(signC_D):factor(isDiff)`
# plot(t$`factor(signC_D):factor(isDiff)`)


```


To-do: Do D < 0 and D > 0 separately

```{r }
#detach("package:plotly", unload = TRUE)
library(ggplot2)
library(ggtern)
library(latex2exp)


datUse = eqDataPos

head(datUse)

# C_s

plotC_s <- ggplot(data = datUse, mapping = aes(x = u1eq, y = u2eq, z = bueq)) + coord_tern(Tlim=c(0,1),Llim=c(0,1),Rlim=c(0,1)) + geom_point(aes(colour = x_pos_invades), size = 5, alpha = 0.5, shape = 1) + theme_bw()
plotC_s <- plotC_s + tern_limits(labels=c(0,0.2, 0.4, 0.6, 0.8, 1)) + labs(x = TeX("$u_1$"), y = TeX("$u_2$"), z = TeX("$\\bar{u}$"),color = TeX("$C_s > 0$")) +theme_legend_position(x = "topleft")  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))  + theme(text = element_text(size = 18))
plotC_s
ggsave("Figures/ternaryAll_C_s.png", plot = plotC_s)

#C_D

plotC_D <- ggplot(data = datUse, mapping = aes(x = u1eq, y = u2eq, z = bueq)) + coord_tern(Tlim=c(0,1),Llim=c(0,1),Rlim=c(0,1)) + geom_point(aes(colour = y_pos_invades), size = 5, alpha = 0.5, shape = 1) + theme_bw()
plotC_D <- plotC_D + tern_limits(labels=c(0,0.2, 0.4, 0.6, 0.8, 1)) + labs(x = TeX("$u_1$"), y = TeX("$u_2$"), z = TeX("$\\bar{u}$"), color = TeX("$C_D > 0$")) +theme_legend_position(x = "topleft")  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
plotC_D
ggsave("Figures/ternaryAll_C_D.png", plot = plotC_D)




```


```{r ternary Unequal}
#detach("package:plotly", unload = TRUE)
library(ggplot2)
library(ggtern)
library(latex2exp)


datUse = eqDataPos
plotD <- ggplot(data = datUse, mapping = aes(x = u1eq, y = u2eq, z = bueq)) + coord_tern(Tlim=c(0,1),Llim=c(0,1),Rlim=c(0,1)) + geom_point(aes(colour = D), size = 5, alpha = 0.5, shape = 1) + theme_bw()
plotD <- plotD + tern_limits(labels=c(0,0.2, 0.4, 0.6, 0.8, 1)) + labs(x = TeX("$u_1$"), y = TeX("$u_2$"), z = TeX("$\\bar{u}$")) +theme_legend_position(x = "topleft") + scale_colour_binned(low='blue', high = 'red') + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
plotD
ggsave("Figures/ternaryAll_bigD.png", plot = plotD)

plotMU <- ggplot(data = datUse, mapping = aes(x = u1eq, y = u2eq, z = bueq)) + coord_tern(Tlim=c(0,1),Llim=c(0,1),Rlim=c(0,1)) + geom_point(aes(colour = mu), size = 3, alpha = 0.5, shape = 1) + theme_bw()
plotMU <- plotMU + tern_limits(labels=c(0,0.2, 0.4, 0.6, 0.8, 1)) + labs(x = TeX("$u_1$"), y = TeX("$u_2$"), z = TeX("$\\bar{u}$"), colour = TeX("$\\mu$")) +theme_legend_position(x = "topleft") + scale_colour_binned(low='blue', high = 'red') + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
plotMU
ggsave("Figures/ternaryAllMU.png", plot = plotMU)

plotd <- ggplot(data = datUse, mapping = aes(x = u1eq, y = u2eq, z = bueq)) + coord_tern(Tlim=c(0,1),Llim=c(0,1),Rlim=c(0,1))+ geom_point(aes(colour = K), alpha = 0.5, size = 3, shape = 1) + theme_bw()
plotd <- plotd + tern_limits(labels=c(0,0.2, 0.4, 0.6, 0.8, 1)) + labs(x = TeX("$u_1$"), y = TeX("$u_2$"), z = TeX("$\\bar{u}$"), legend = 'd') +theme_legend_position(x = "topleft") + scale_colour_binned(low='blue', high = 'red') + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))

plotd
ggsave("Figures/ternaryAll_K.png", plot = plotd)

plotBeta <- ggplot(data = datUse, mapping = aes(x = u1eq, y = u2eq, z = bueq)) + coord_tern(Tlim=c(0,1),Llim=c(0,1),Rlim=c(0,1))+ geom_point(aes(colour = beta), alpha = 0.5, size = 3, shape = 1) + theme_bw()
plotBeta <- plotBeta + tern_limits(labels=c(0,0.2, 0.4, 0.6, 0.8, 1)) + labs(x = TeX("$u_1$"), y = TeX("$u_2$"), z = TeX("$\\bar{u}$"), colour = TeX("$\\beta$")) + theme_legend_position(x = "topleft") + scale_colour_binned(low='blue', high = 'red') + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
plotBeta
ggsave("Figures/ternaryAllbeta.png", plot = plotBeta)


```